---
title: Reproducibility
output:
  github_document
---

```{r setup, echo=FALSE}
# save the built-in output hook
hook_output <- knitr::knit_hooks$get("output")

# set a new output hook to truncate text output
knitr::knit_hooks$set(output = function(x, options) {
  if (!is.null(n <- options$out.lines)) {
    x <- xfun::split_lines(x)
    if (length(x) > n) {
      # truncate the output
      x <- c(head(x, n/2), '....', tail(x, n/2 + 1))
    }
    x <- paste(x, collapse = "\n")
  }
  hook_output(x, options)
})
```

As documented elsewhere, TGVE is a `geoplumber` application and therefore there is a particular directory structure to it. That is R at the backend based on `plumber` APIs and fronted being a CRA app.

This document shows how TGVE is a fully reproducible using R code. This markdown document itself is prodcued using Rmarkdown companion document.

```{r}
# we need goeplumber
# & curl
library(geoplumber)
library(RCurl)
message("geoplumber v: ", packageVersion("geoplumber"))

# create a geoplumber test app
d <- file.path(tempdir(), "gp")
gp_create(d)
od <- setwd(d)
stopifnot(gp_is_wd_geoplumber())

# download some data
download.file("https://github.com/saferactive/saferactive/releases/download/0.1/london_junction_point_cas.geojson",
              destfile = "london.geojson")
# pass it to geoplumber's `gp_explore` as an sf object
ps <- gp_explore(sf = sf::st_read("london.geojson"), build = F)
# wait for plumber to start
Sys.sleep(2)
ps

# is the API endpoint serving?
gpExploreURL <- "http://localhost:8000/api/explore"
webpage <- getURL(gpExploreURL)
webpage <- readLines(tc <- textConnection(webpage)); close(tc)
# expercting start of geojson object
substr(tail(webpage)[1],start = 1, stop=50)

# navigate to the build (not built)
gpURL <- "http://localhost:8000/"
webpage <- getURL(gpURL)
webpage <- readLines(tc <- textConnection(webpage)); close(tc)
tail(webpage)
# we know first line of the tail is the warning message from geoplumber
all(grepl("build missing", tail(webpage)[1]), ignore.case = TRUE)

# cleanup
setwd(od)
ps$kill()
```

As we can see from the output of the R chunk, we do the following:

1. Create a clean geoplumber instance
2. Download some data
3. Read (2) and pass it to `gp_explore`
4. Do some extra checks on the app.

## Front-end

We can follow standard CRA app commands, though the TGVE repository may have slightly different `scripts` defined. The `geoplumber` commands (functions) related to the front-end also should work as shown below:
```{r, out.lines=4}
od <- setwd(d)
stopifnot(gp_is_wd_geoplumber())
# npm run build
# or
gp_build()
```




